Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-16 exp1/present2013.tex
reintroduce questions, just in case
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@687 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\begin{frame}{Questions to ask}

\begin{enumerate}
\item Are there factors that cover all realistic features?
\item If not, are they adequately covered by randomization?
\item If so, would the variance resulting from randomization obscure
  factors that could provide clues that the levels are wrongly set?
\item By carefully examining interactions with ``Implement'', are
  there any that are unaccounted for, and that could point out wrongly
  set levels?
\end{enumerate}
